### 2015-01-30 ASP.tex
fixes in section ASP
style of the tools names

According to \cite{baral2003knowledge}, the alphabet of ASP is composed of seven classes of symbols:
\begin{itemize}
  \item \emph{constants}, symbols of \emph{functions} and symbols of \emph{predicates} are composed of letters and start with a lowercase letter,
  \item \emph{variables} follow the same rule but start with a capital letter,
  \item \emph{connectors} that are “$\neg$”, “$\textbf{or}$”, “$\leftarrow$”, “$\textbf{not}$” and “$,$”,
  \item \emph{punctuation} that can be “(”, “)” and “.”,
  \item the special symbols “$\bot$” and “$\top$”.
\end{itemize}

@@

\item \textbf{The rules:}
A rule has the following form:
\begin{equation} \label{eq1ASP}
 head \leftarrow body.
\end{equation}
which is equivalent to:
\begin{equation} \label{eq2ASP}
l_{0} \leftarrow l_{1},...,l_{m}, \ASPnot l_{m+1},..., \ASPnot l_{n}.
\end{equation}
where $l_{i}$ are literals for all $i \in \llbracket 1 ; n \rrbracket$, and $0 \leq m \leq n$.
This rule states:
\[
\left.
    \begin{array}{ll}
        \text{If} ~ l_{1},...,l_{m}  ~ \text{are \textbf{true}}\\
        \text{and} ~ l_{m+1},...,l_{n} ~ \text{are \textbf{false}}
    \end{array}
\right \} \text{Then} ~ l_{0} ~ \text{is } \textbf{true}.
\]

@@

Therefore, in practice, the solving of ASP programs relies on a \emph{grounder} and a \emph{solver}
that usually work together:
first the grounder is used to remove variables in order to achieve an equivalent but constant program,
then the solver computes all answer sets for this stabilized program~\cite{Vladimir,AnsPrologAPE}.
Amongst all available grounders for ASP, we can name
\texttt{Gringo}, \texttt{DLV} and \texttt{LParse},
and the solvers include
\texttt{SModels}, \texttt{DLV}, \texttt{CModels}, \texttt{Clasp}...

For the work presented in this paper, we worked with \texttt{Clingo} (version 3) which is a combination of the grounder \texttt{Gringo} and the solver \texttt{Clasp}.

>>>>

According to \cite{baral2003knowledge}, the alphabet of ASP is composed of seven classes of symbols:
\begin{itemize}
  \item \emph{constants}, symbols of \emph{functions} and symbols of \emph{predicates} are composed of letters and start with a lowercase letter,
  \item \emph{variables} follow the same rule but start with a capital letter,
  \item \emph{connectors} that are “$\leftarrow$”, “$\textbf{not}$” and “$,$”,
  \item \emph{punctuation} that can be “(”, “)” and “.”,
  \item the special symbols “$\bot$” and “$\top$”.
\end{itemize}

@@

\item \textbf{The rules:}
A rule has the following form:
\begin{equation} \label{eq1ASP}
 head \leftarrow body.
\end{equation}
which is equivalent to:
\begin{equation} \label{eq2ASP}
l_{0} \leftarrow l_{1},...,l_{m}, \ASPnot l_{m+1},..., \ASPnot l_{n}.
\end{equation}
where $l_{i}$ are literals for all $i \in \llbracket 1 ; n \rrbracket$, and $0 \leq m \leq n$.
This rule states:
\[
\left.
    \begin{array}{rcl}
        \text{If } & l_{1},...,l_{m}  & \text{ \textbf{can} be proved true}\\
        \text{and } & l_{m+1},...,l_{n} & \text{ \textbf{cannot} be proved true}
    \end{array}
\right \} \text{Then} ~ l_{0} ~ \text{is } \textbf{true}.
\]

@@

Therefore, in practice, the solving of ASP programs relies on a \emph{grounder} and a \emph{solver}
that usually work together:
first the grounder is used to remove variables in order to achieve an equivalent but constant program,
then the solver computes all answer sets for this stabilized program~\cite{Vladimir,AnsPrologAPE}.
Amongst all available grounders for ASP, we can name
\textsc{Gringo}, \textsc{DLV} and \textsc{LParse},
and the solvers include
\textsc{SModels}, \textsc{DLV}, \textsc{CModels}, \textsc{Clasp}...

For the work presented in this paper, we worked with \textsc{Clingo} (version 3) which is a combination of the grounder \textsc{Gringo} and the solver \textsc{Clasp}.
